---
title: "Trading Frequency"
output: html_notebook
---

# import files
```{r}
library(tidyverse)
library(lubridate)

# summary1 <- read.csv("data/summary1.txt")
# # head(summary1)
# summary1 <- summary1[,-1]
# 
# header <- read.csv("data/summary1 header.txt")
# header <- header[,"Aggregation_Count"]
# 
# colnames(summary1) <- header
# 
# summary1$Insider_Company_ID <- paste0(summary1$SEC_Insider_ID, ",", summary1$SEC_Company_ID)
# summary1$`beating sector` <- ifelse(summary1$Position * summary1$net_return_1yr > 0,1,0)
# summary1$Date <-  as.Date(paste(summary1$Year,summary1$Month,summary1$Day,sep="-"))
# summary1 <-  subset(summary1,select = -c(Year,Month,Day))
# 
# summary1 <- summary1 %>%
#                 select(Insider_Company_ID, `beating sector`, Date,SEC_Insider_ID, SEC_Company_ID, `Position (Buy or Sell)`, `Options (Option related or not)`)

# save(summary1, file = "data/summary1.RData")
load("data/summary1.RData")
```

# 1 out of 1
```{r}
trans_once <- summary1 %>%
        group_by(Insider_Company_ID) %>%
        count() %>%
        filter(n == 1)
trans_once <- trans_once$Insider_Company_ID

summary_once <- summary1 %>%
        filter(Insider_Company_ID %in% trans_2)

tot_once <- nrow(summary_once)
success_once <- sum(summary_once$`beating sector`)
success_rate_once <- success_once / tot_once * 100
success_rate_once
```

# 2 out of 2
```{r}
trans_2 <- summary1 %>%
        group_by(Insider_Company_ID) %>%
        count() %>%
        filter(n == 2)

trans_2 <- trans_2$Insider_Company_ID

summary_twice <- summary1 %>%
        filter(Insider_Company_ID %in% trans_2) %>%
        group_by(Insider_Company_ID) %>%
        mutate(sum_beat_sector = sum(`beating sector`)) %>%
        arrange(Insider_Company_ID) %>%
        filter(sum_beat_sector == 2)

head(summary_twice)

tot_2 <- length(trans_2)
success_2 <- nrow(summary_twice) / 2
success_rate_2 <- success_2 / tot_2 * 100
success_rate_2
```

# 3 out of 4 or better
```{r}
trans_3_4 <- summary1 %>%
        group_by(Insider_Company_ID) %>%
        count() %>%
        filter(n == 4)
nrow(trans_3_4)


trans_3_4 <- trans_3_4$Insider_Company_ID

summary_3_4 <- summary1 %>%
        filter(Insider_Company_ID %in% trans_3_4) %>%
        group_by(Insider_Company_ID) %>%
        mutate(sum_beat_sector = sum(`beating sector`)) %>%
        arrange(Insider_Company_ID) %>%
        filter(sum_beat_sector == 3 | sum_beat_sector == 4)

head(summary_3_4, 15)
nrow(summary_3_4)

tot_3_4 <- length(trans_3_4)
success_3_4 <- nrow(summary_3_4) / 4
success_rate_3_4 <- success_3_4 / tot_3_4 * 100
success_rate_3_4
```

# tranding frequency success rate function
```{r}
trad_freq_success_func <- function(summary1, numerator, denominator) {
        library(tidyverse)
        
        trans_insiders <- summary1 %>%
                        group_by(Insider_Company_ID) %>%
                        count() %>%
                        filter(n == denominator)
        
        
        trans_insiders <- trans_insiders$Insider_Company_ID
        
        summary <- summary1 %>%
                filter(Insider_Company_ID %in% trans_insiders) %>%
                group_by(Insider_Company_ID) %>%
                mutate(sum_beat_sector = sum(`beating sector`)) %>%
                arrange(Insider_Company_ID) 
        
        if ((denominator - numerator) == 0) {       
                summary <- summary %>%
                        filter(sum_beat_sector == numerator)
                expected_success <- choose(denominator, numerator) * 0.5^numerator
        } else if ((denominator - numerator) == 1) {
                summary <- summary %>%
                        filter(sum_beat_sector == numerator | sum_beat_sector == (numerator + 1) )
                expected_success <- choose(denominator, numerator) * 0.5^numerator * 0.5^(1) + choose(denominator, numerator + 1) * 0.5^(numerator + 1) 
        } else if ((denominator - numerator) == 2) {
                summary <- summary %>%
                        filter(sum_beat_sector == numerator | sum_beat_sector == (numerator + 1) | sum_beat_sector == (numerator + 2) )
                expected_success <- choose(denominator, numerator) * 0.5^numerator * 0.5^(2) + choose( denominator, numerator + 1) * 0.5^(numerator + 1) * 0.5^(1) + choose(denominator, numerator + 2) * 0.5^(numerator + 2) 
        } else if ((denominator - numerator) == 3) {
                summary <- summary %>%
                        filter(sum_beat_sector == numerator | sum_beat_sector == (numerator + 1) | sum_beat_sector == (numerator + 2) | sum_beat_sector == (numerator + 3) )  
                expected_success <- choose(denominator, numerator) * 0.5^numerator * 0.5^(3) + choose( denominator, numerator + 1) * 0.5^(numerator + 1) * 0.5^(2) + choose(denominator, numerator + 2) * 0.5^(numerator + 2) * 0.5^(1) + choose(denominator, numerator + 3) * 0.5^(numerator + 3)
        }        
        
        tot <- length(trans_insiders)
        success <- nrow(summary) / denominator 
        success_rate <- success / tot * 100
        
         
        
        df <- data.frame("Expected_Success_Rate" = round(expected_success * 100, 3), "Successful_Insiders" = success, "All_Insiders" = tot, "Actual_Success_Rate" = round(success_rate,3))
        df$Actual_vs_Expected <- (df$Actual_Success_Rate / df$Expected_Success_Rate) - 1
        df$Actual_vs_Expected <- round(df$Actual_vs_Expected * 100, 3)
        
        rownames(df) <- paste0(numerator, " out of ", denominator)
       
        return(df)
}
```

```{r}
trad_freq_success_func(summary1, 3, 4)
```

# Replicate Trading Frequency Table

## Perfect Records vs Benchmarks
```{r}
# for (i in 1:10) {
#         if (i == 1) {
#                 df <- trad_freq_success_func(summary1, i, i)
#         } else {
#                 df <- rbind(df, trad_freq_success_func(summary1, i, i))
#         }
# }
# df <- as.data.frame(df)
# 
# df

# save(df, file = "data/df.RData")
load("data/df.RData")
```

## One Underperforming Transaction
```{r}
for (i in 1:8) {
        if (i == 1) {
                df_1 <- trad_freq_success_func(summary1, i + 1, i + 2)
        } else {
                df_1 <- rbind(df_1, trad_freq_success_func(summary1, i + 1, i + 2))
        }
}
df_1 <- as.data.frame(df_1)

df_1

# save(df_1, file = "data/df_1.RData")
load("data/df_1.RData")
```


## Two Underperforming Transactions
```{r}
for (i in 1:6) {
        if (i == 1) {
                df_2 <- trad_freq_success_func(summary1, i + 2, i + 4)
        } else {
                df_2 <- rbind(df_2, trad_freq_success_func(summary1, i + 2, i + 4))
        }
}
df_2 <- as.data.frame(df_2)

df_2

# save(df_2, file = "data/df_2.RData")
load("data/df_2.RData")
```


## Three Underperforming Transactions
```{r}
for (i in 1:4) {
        if (i == 1) {
                df_3 <- trad_freq_success_func(summary1, i + 3, i + 6)
        } else {
                df_3 <- rbind(df_3, trad_freq_success_func(summary1, i + 3, i + 6))
        }
}
df_3 <- as.data.frame(df_3)

df_3

# save(df_3, file = "data/df_3.RData")
load("data/df_3.RData")
```

## Put together DFs
```{r}
# library(data.table)
# df_4 <- rbindlist(list(df, df_1, df_2, df_3))
df_4 <- do.call("rbind",list(df, df_1, df_2, df_3))
View(df_4)

library(xlsx)
write.xlsx(df_4, "data/Trading_Frequency_vs_Performance.xlsx")
```


# Buy and Sell Trading Frequency

## 1 Trials/Person
```{r}
library(tidyverse)

trans_insiders <- summary1 %>%
                group_by(Insider_Company_ID) %>%
                count() %>%
                filter(n == 1)

trans_insiders <- trans_insiders$Insider_Company_ID

summary <- summary1 %>%
        filter(Insider_Company_ID %in% trans_insiders) %>%
        group_by(Insider_Company_ID) %>%
        mutate(sum_beat_sector = sum(`beating sector`)) %>%
        arrange(Insider_Company_ID) 
head(summary)

sells <- summary %>%
                filter(sum_beat_sector == 1, `Position (Buy or Sell)` == -1)
head(sells)

buys <- summary %>%
                filter(sum_beat_sector == 1, `Position (Buy or Sell)` == 1)
head(buys)

tot_sells <- sum(summary$`Position (Buy or Sell)` == -1)

tot_buys <- sum(summary$`Position (Buy or Sell)` == 1)

success_sells <- nrow(sells) / tot_sells  

success_buys <- nrow(buys) / tot_buys

```


## 2 Trials/Person
```{r}
library(tidyverse)

trans_insiders_2 <- summary1 %>%
                group_by(Insider_Company_ID) %>%
                count() %>%
                filter(n == 2)
head(trans_insiders_2)

trans_insiders_2 <- trans_insiders_2$Insider_Company_ID

summary_2 <- summary1 %>%
        filter(Insider_Company_ID %in% trans_insiders_2) %>%
        group_by(Insider_Company_ID) %>%
        mutate(sum_beat_sector = sum(`beating sector`)) %>%
        arrange(Insider_Company_ID) 
head(summary_2)

sells_2 <- summary_2 %>%
                filter(sum_beat_sector !=  0, `Position (Buy or Sell)` == -1)
head(sells)

buys_2 <- summary_2 %>%
                filter(sum_beat_sector !=  0, `Position (Buy or Sell)` == 1)
head(buys)

tot_sells_2 <- sum(summary_2$`Position (Buy or Sell)` == -1)

tot_buys_2 <- sum(summary_2$`Position (Buy or Sell)` == 1)

success_sells_2 <- nrow(sells_2) / tot_sells_2  

success_buys_2 <- nrow(buys_2) / tot_buys_2

head(summary_2)
```

# trading frequency buy/sell success rate function
```{r}
trad_freq_buy_sell_success_func <- function(summary1, trials) {
        library(tidyverse)
        
        trans_insiders <- summary1 %>%
                        group_by(Insider_Company_ID) %>%
                        count() %>%
                        filter(n == trials)
        
        
        trans_insiders <- trans_insiders$Insider_Company_ID
        
        summary <- summary1 %>%
                filter(Insider_Company_ID %in% trans_insiders) %>%
                group_by(Insider_Company_ID) %>%
                mutate(sum_beat_sector = sum(`beating sector`)) %>%
                arrange(Insider_Company_ID) 
        
        sells <- summary %>%
                        filter(sum_beat_sector !=  0, `Position (Buy or Sell)` == -1)

        buys <- summary %>%
                        filter(sum_beat_sector !=  0, `Position (Buy or Sell)` == 1)
        
        tot_sells <- sum(summary$`Position (Buy or Sell)` == -1)
        
        tot_buys <- sum(summary$`Position (Buy or Sell)` == 1)
        
        success_sells <- nrow(sells) / tot_sells 
        
        success_buys <- nrow(buys) / tot_buys
        
        
        # if ((denominator - numerator) == 0) {       
        #         summary <- summary %>%
        #                 filter(sum_beat_sector == numerator)
        #         expected_success <- choose(denominator, numerator) * 0.5^numerator
        # } else if ((denominator - numerator) == 1) {
        #         summary <- summary %>%
        #                 filter(sum_beat_sector == numerator | sum_beat_sector == (numerator + 1) )
        #         expected_success <- choose(denominator, numerator) * 0.5^numerator * 0.5^(1) + choose(denominator, numerator + 1) * 0.5^(numerator + 1) 
        # } else if ((denominator - numerator) == 2) {
        #         summary <- summary %>%
        #                 filter(sum_beat_sector == numerator | sum_beat_sector == (numerator + 1) | sum_beat_sector == (numerator + 2) )
        #         expected_success <- choose(denominator, numerator) * 0.5^numerator * 0.5^(2) + choose( denominator, numerator + 1) * 0.5^(numerator + 1) * 0.5^(1) + choose(denominator, numerator + 2) * 0.5^(numerator + 2) 
        # } else if ((denominator - numerator) == 3) {
        #         summary <- summary %>%
        #                 filter(sum_beat_sector == numerator | sum_beat_sector == (numerator + 1) | sum_beat_sector == (numerator + 2) | sum_beat_sector == (numerator + 3) )  
        #         expected_success <- choose(denominator, numerator) * 0.5^numerator * 0.5^(3) + choose( denominator, numerator + 1) * 0.5^(numerator + 1) * 0.5^(2) + choose(denominator, numerator + 2) * 0.5^(numerator + 2) * 0.5^(1) + choose(denominator, numerator + 3) * 0.5^(numerator + 3)
        # }        
         
        
        df <- data.frame("Successful_Trials_Buys" = nrow(buys), "All_Trials_Buys" = tot_buys, "Actual_Success_Rate_Buys" = round(success_buys,3), "Successful_Trials_Sells" = nrow(sells), "All_Trials_Sells" = tot_sells, "Actual_Success_Rate_Sells" = round(success_sells,3))
        # df$Actual_vs_Expected <- (df$Actual_Success_Rate / df$Expected_Success_Rate) - 1
        # df$Actual_vs_Expected <- round(df$Actual_vs_Expected * 100, 3)
        
        rownames(df) <- paste0(trials," Trials")
       
        return(df)
}
```

# 2 trials / buy & sell
```{r}
trad_freq_buy_sell_success_func(summary1, 2)
```

